---
title: "Project 5"
subtitle: "Creating data from digital sources"
author: "Stefan Walles (swal435)"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, message=FALSE, warning=FALSE, error=FALSE)
```

``` {css, echo = FALSE}
body {
  background-color: #ebf5ff;
  margin-top: 30px;
  margin-bottom: 30px;
  font-family: Verdana;
}
#header {
  background-color: #056cb0;
  color: white;
  padding: 20px;
  text-align: center;
  border-style: solid;
  border-color: black;
  border-radius: 25px;
}
h2 {
  background-color: white;
  text-align: center;
  padding: 10px;
  border-style: solid;
  border-color: white;
  border-radius: 25px;
}
hr {
  border: 2px solid black;
}
img {
  border-radius: 8px;
  display: block;
  margin-left: auto;
  margin-right: auto;
  width: 75%;
}
```

## Part A

The data context I selected was the differences between different types of cat breeds. I have three cats at home each with their own personalities. I was interested in finding out what effect breed had on a cat's personality. I found a website that facilitates the adoption of cats which had information on different cat breeds and their personalities. So that is what I used for part A.

```{r file='partA.R'}

```

## Part B

```{r file='partB.R', results='hide'}

```

I investigated four aspects with regards to Minister Hon Erica Stanford's releases:

- On average her releases have `r mean_number_of_words` words.
- On average each paragraph in the releases contained `r mean_number_of_words_per_paragraph` words.
- I noticed that her releases were quite quote heavy. On average each release contained `r mean_number_of_quotes` quotes.
- Minister Hon Erica Stanford is the minister for education and immigration.However,  `r percentage_of_education_releases`% of her releases are about education.

## Part C

```{r file='partC.R'}

```

From the visualisation we can clearly see that Education was a very popular topic, in the past, compared to data and immigration, but that it has become less popular in more recent years.

## Learning Reflextion

The thing I most enjoyed learning about in this module was web scraping. I think it is really important as it allows you access to stores of information that otherwise would be very cumbersome to collect or get access to. I do however recognise my responsibility to make sure that I am allowed to scrape data before I do so.

During Task A I ran into a problem where search results were distributed over several pages, but the URLs for each of these pages would return the same results. In the end I only used results from the first page. I would like to expand my knowledge about web scraping and websites in general to be able to fix similar issues in the future.

## Self Review

Thinking back I learned a lot while working on the 5 projects for this course. 

One thing that I really enjoyed learning about was creating plots using ggplots2. I have learned how to create many different kinds of plots and how to customise them to fit my needs.

Another important thing I learned was about collecting and using data from digital sources. In project 1 we used a Google form together with a published Google document to collect data and report on it in a dynamic way. For project 4 we used an API and for project 5 we used web scraping. These concepts allows me to easily access data that otherwise could have been difficult to obtain.

Learning outcome 5: "Select and combine a range of data technologies, including HTML and CSS for reporting and web scraping" describes what I believe is the most important thing that I have learned. Using and taking advantage of these technologies not only makes things easier, but also allows for more effective reporting and communication.
